\centering{Follow up on the incoherent t, t'}

### 2017-07-07 for_eg6_group/Final_t_tprime_work/Incoh.tex
some cleaning

\begin{figure}[h!]
\centering
\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_1.pdf}
\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_2.pdf}
\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_3.pdf}
\caption{On top and middle: $t-t'$ as a function of $t'$ for the E1-DVCS2 free 
proton DVCS sample BEFORE correcting $t'$. On bottom: $t$ versus $t'$.  The red 
lines are proposed correction functions for $t'$.}
\label{fig:corrections_tprime_e1dvcs2}
\end{figure}

>>>>

\begin{figure}[h!]
\centering
%\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_1.pdf}
\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_2.pdf}
\includegraphics[height=7.0cm]{fig/h_tprimet_t_InCoh_3.pdf}
\caption{On top: $t-t'$ as a function of $t'$ for the E1-DVCS2 free proton DVCS 
sample BEFORE correcting $t'$. On bottom: $t$ versus $t'$. The red lines are 
proposed first and second correction functions for $t'$.}
\label{fig:corrections_tprime_e1dvcs2}
\end{figure}
